---
title: "Stevie's Senior Thesis"
output: html_notebook
---

Load libraries
```{r}
setwd("~/senior_thesis/)

source('libraries.R')
source('get_nc.R')

```

Download data files
```{r}
model.list = c("HadGEM3-GC31-LL","EC-Earth3", "MRI-ESM2-0", "NorESM2-LM", "NorESM2-MM", "CMCC-CM2-SR5", "AWI-CM-1-1-MR")
lapply(model.list, get_nc)
#system("az vm deallocate --name atlantisserver01 --no-wait --resource-group morzariacedogroup")

#get_nc(model.name = "AWI-CM-1-1-MR")

```

Using epwshiftr to specify which files to download
```{r}
# NOTE: epwshiftr package does not work with this version of R (3.6.3), so I had to run this section in a different server

# set directory to store files
options(epwshiftr.dir = tempdir())
options(epwshiftr.verbose = TRUE)

# get CMIP6 data nodes
(nodes <- get_data_node())

# create a CMIP6 output file index
idx <- init_cmip6_index(
  # only consider ScenarioMIP activity
  activity = "ScenarioMIP",
  
  # specify variables POC, NPP, and MLD
  variable = c("epc100"),
  
  # specify report frequency
  frequency = "mon",
  
  # specify experiment name
  experiment = c("ssp585"),
  
  # specify GCM names
  source = c("CMCC-ESM2"),
  
  # specify variant,
  variant = "r1i1p1f1",
  
  # save to data directory
  save = FALSE
)

#
df <- idx[,21]
#saving CMIP6 data list
write.csv(df,"~/senior_thesis/download_indexes/cmip6_index2.csv", row.names = TRUE)

```

Download data files
```{r}

source('get_nc_thredds.R')

#creating save path
save.path <- "~/senior_thesis/cmip6_data"
dir.create(save.path)

#first attempt (got CESM2, CESM2-WACCM, MPI-ESM1-2-HR)
cmip6.index <- read_csv("~/senior_thesis/download_indexes/cmip6_index.csv")
get_nc_thredds(cmip6.index, save.path)

#GFDL download (only MLD)
cmip6.index <- read_csv("~/senior_thesis/download_indexes/cmip6_index_gfdl.csv")
get_nc_thredds(cmip6.index, save.path)

#GFDL download - manually pasted file urls from ESGF search query, failed to connect to node and could not download
cmip6.index <- read_csv("~/senior_thesis/download_indexes/gfdl_urls.csv")
get_nc_thredds(cmip6.index, save.path)

#IPSL download - failed because it could not connect to vesg.ipsl.upmc.fr data node
cmip6.index <- read_csv("~/senior_thesis/download_indexes/cmip6_index_ipsl.csv")
get_nc_thredds(cmip6.index, save.path)

#UKESM download - manually pasted file urls from ESGF search query
cmip6.index <- read_csv("~/senior_thesis/download_indexes/ukesm_urls.csv")
get_nc_thredds(cmip6.index, save.path)

#missing files download
cmip6.index <- read_csv("~/senior_thesis/download_indexes/cmip6_index_gfdl_epc100.csv")
get_nc_thredds(cmip6.index, save.path)

#GFDL mlotst gr
cmip6.index <- read_csv("~/senior_thesis/download_indexes/gfdl_mlotst.csv")
get_nc_thredds(cmip6.index, save.path)

#Download EC Earth,CMCC
cmip6.index <- read_csv("~/senior_thesis/download_indexes/cmip6_index2.csv")
get_nc_thredds(cmip6.index, save.path)

#Download areacello data for all models but CESM (already downloaded)

```

Combine multipart files into a single nc file
```{r}
## CESM Combine ----------

# list of all files with gr: "data reported on a model's regular grid"
model.files <- list.files("~/senior_thesis/CESM_data/", pattern = "*_gn_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/senior_thesis/CESM_data/", pattern = "*_gn_*.*nc$") %>% 
  str_split(.,"_gn") %>% 
  unlist %>% 
  #switch between variables and model reps here. You can do this manually here, then rerun. ( Note on 2/8/21)
  grep("mlotstmax_Omon_CESM2_ssp585_r10i1p1f1",., value = TRUE) %>% 
  unique()

data.path <- "~/senior_thesis/CESM_data/"
save.path <- "~/senior_thesis/combined_CESM_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)

## GFDL Combine -----------
model.files <- list.files("~/senior_thesis/GFDL_data/", pattern = "*_gr_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/senior_thesis/GFDL_data/", pattern = "*_gr_*.*nc$") %>% 
  str_split(.,"_gr") %>% 
  unlist %>% 
  #switch between variables and model reps here. You can do this manually here, then rerun. ( Note on 2/8/21)
  grep("mlotst_Omon_GFDL-ESM4_ssp585_r1i1p1f1",., value = TRUE) %>% 
  unique()

data.path <- "~/senior_thesis/GFDL_data/"
save.path <- "~/senior_thesis/combined_GFDL_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)

## UKESM Combine ----------

# list of all files with gr: "data reported on a model's regular grid"
model.files <- list.files("~/senior_thesis/UKESM_data/", pattern = "*_gn_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/senior_thesis/UKESM_data/", pattern = "*_gn_*.*nc$") %>% 
  str_split(.,"_gn") %>% 
  unlist %>% 
  #switch between variables and model reps here. You can do this manually here, then rerun. ( Note on 2/8/21)
  grep("expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2",., value = TRUE) %>% 
  unique()

data.path <- "~/senior_thesis/UKESM_data/"
save.path <- "~/senior_thesis/combined_UKESM_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)

##EC Earth Combine --------

# list of all files with gr: "data reported on a model's regular grid"
model.files <- list.files("~/senior_thesis/EC_Earth_data/", pattern = "*_gn_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/senior_thesis/EC_Earth_data/", pattern = "*_gn_*.*nc$") %>% 
  str_split(.,"_gn") %>% 
  unlist %>% 
  #switch between variables and model reps here. You can do this manually here, then rerun. ( Note on 2/8/21)
  grep("expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1",., value = TRUE) %>% 
  unique()

data.path <- "~/senior_thesis/EC_Earth_data/"
save.path <- "~/senior_thesis/combined_EC-Earth_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)

##MPI Combine --------

# list of all files with gr: "data reported on a model's regular grid"
model.files <- list.files("~/senior_thesis/MPI_data/", pattern = "*_gn_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/senior_thesis/MPI_data/", pattern = "*_gn_*.*nc$") %>% 
  str_split(.,"_gn") %>% 
  unlist %>% 
  #switch between variables and model reps here. You can do this manually here, then rerun. ( Note on 2/8/21)
  grep("mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1",., value = TRUE) %>% 
  unique()

data.path <- "~/senior_thesis/MPI_data/"
save.path <- "~/senior_thesis/combined_MPI_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)

##UKESM Combine (just for the later files) -----------

model.files <- list.files("~/senior_thesis/UKESM_data/expc_late", pattern = "*_gn_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/senior_thesis/UKESM_data/expc_late", pattern = "*_gn_*.*nc$") %>% 
  str_split(.,"_gn") %>% 
  unlist %>% 
  #switch between variables and model reps here. You can do this manually here, then rerun. ( Note on 2/8/21)
  grep("expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2",., value = TRUE) %>% 
  unique()

data.path <- "~/senior_thesis/UKESM_data/expc_late"
save.path <- "~/senior_thesis/combined_UKESM_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)

```


Get metadata for combined files
```{r}
source('grab_metadata.R')

#CESM
grab_metadata(data.path = "~/senior_thesis/combined_CESM_files",
              model.files = list.files("~/senior_thesis/combined_CESM_files/"))

#GFDL
grab_metadata(data.path = "~/senior_thesis/combined_GFDL_files",
              model.files = list.files("~/senior_thesis/combined_GFDL_files/"))

#MPI
grab_metadata(data.path = "~/senior_thesis/combined_MPI_files",
              model.files = list.files("~/senior_thesis/combined_MPI_files/"))

#CMCC
grab_metadata(data.path = "~/senior_thesis/combined_CMCC_files",
              model.files = list.files("~/senior_thesis/combined_CMCC_files/"))

#EC-Earth
grab_metadata(data.path = "~/senior_thesis/combined_EC-Earth_files",
              model.files = list.files("~/senior_thesis/combined_EC-Earth_files/"))

#UKESM
grab_metadata(data.path = "~/senior_thesis/combined_UKESM_files",
              model.files = list.files("~/senior_thesis/combined_UKESM_files/"))


```


Calculate short-term (2014-2034) and long-term (2079-2099) average downward flux of POC at 100m
units: (mol m-2 y-1)
```{r}
setwd("~/senior_thesis/")

source('calc_epc100_avg.R')
source('get_time.R')

options(max.print = 2000)

## CESM --------------

get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'epc100_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc')
#start date = 09/14/13
#end date = 07/24/99

calc_epc100_avg(data.path = "~/senior_thesis/combined_CESM_files/",
                file.name = 'epc100_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc',
                start.st = c(1,1,17),
                start.lt = c(1,1,774),
                save.name = "CESM_epc100_avg")


##CMCC -----------

get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'epc100_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc')
#start date = 12/07/14
#end date = 10/16/00

calc_epc100_avg(data.path = "~/senior_thesis/combined_CMCC_files/",
                file.name = 'epc100_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc',
                start.st = c(1,1,2),
                start.lt = c(1,1,759),
                save.name = "CMCC_epc100_avg")

##EC-Earth ------------

get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'epc100_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc')
#start date = 01/16/15
#end date = 12/16/00

calc_epc100_avg(data.path = "~/senior_thesis/combined_EC-Earth_files/",
                file.name = 'epc100_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc',
                start.st = c(1,1,1),
                start.lt = c(1,1,757),
                save.name = "EC-Earth_epc100_avg")

##GFDL --------------
get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'epc100_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc')
#start date = 12/07/14
#end date = `10/16/00

calc_epc100_avg(data.path = "~/senior_thesis/combined_GFDL_files/",
                file.name = 'epc100_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc',
                start.st = c(1,1,2),
                start.lt = c(1,1,759),
                save.name = "GFDL_epc100_avg")

## MPI --------------
get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'epc100_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc')
#start date = 01/16/15
#end date = `12/16/00

calc_epc100_avg(data.path = "~/senior_thesis/combined_MPI_files/",
                file.name = 'epc100_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc',
                start.st = c(1,1,1),
                start.lt = c(1,1,637),
                save.name = "MPI_epc100_avg")

## UKESM --------
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'epc100_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc')
#start date = 09/03/12
#end date = `05/10/97
#the times on this one are averaged from 01/2077 - 01/2097 instead of 01/2078 - 01/2079 like the other models
get_time(data.path = "~/senior_thesis/UKESM_data/", file.name = 'expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_210001-210012.nc')

calc_epc100_avg(data.path = "~/senior_thesis/combined_UKESM_files/",
                file.name = 'epc100_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc',
                start.st = c(1,1,30),
                start.lt = c(1,1,788),
                save.name = "UKESM_epc100_avg")
```


Plot 3 panel figure showing short-term (2014-2034), long-term (2079-2099), and difference in average downward flux of POC at 100m
```{r}
setwd("~/senior_thesis/")
source('plot_epc100_avg.R')

#CMCC
plot_epc100_avg(wd = "~/senior_thesis/combined_CMCC_files",
                nc_file='epc100_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc',
                 model.name = "CMCC",
                lat.name = "latitude",
                lon.name = "longitude")

#CESM
plot_epc100_avg(wd = "~/senior_thesis/combined_CESM_files",
                nc_file='epc100_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc',
                 model.name = "CESM",
                lat.name = "nlat",
                lon.name = "nlon")

#EC-Earth
plot_epc100_avg(wd = "~/senior_thesis/combined_EC-Earth_files",
                nc_file='epc100_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc',
                 model.name = "EC-Earth",
                lat.name = "latitude",
                lon.name = "longitude")

#GFDL
plot_epc100_avg(wd = "~/senior_thesis/combined_GFDL_files",
                nc_file='epc100_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc',
                 model.name = "GFDL",
                lat.name = "lat",
                lon.name = "lon")

#MPI - make sure to go in and uncomment the scale_y_continuous lines or else this will plot upside down
plot_epc100_avg(wd = "~/senior_thesis/combined_MPI_files",
                nc_file='epc100_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc',
                 model.name = "MPI",
                lat.name = "latitude",
                lon.name = "longitude")

#UKESM
plot_epc100_avg(wd = "~/senior_thesis/combined_UKESM_files",
                nc_file='epc100_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc',
                 model.name = "UKESM",
                lat.name = "latitude",
                lon.name = "longitude")
```


Plot 6 panel figure showing change in average POC flux at 100m in 6 models
```{r}
#run this in a R script, for some reason readPNG doesn't work in the notebook

setwd("~/senior_thesis/figures/")
A <- readPNG('CESM_epc100_change.png')
B <- readPNG('CMCC_epc100_change.png')
C <- readPNG('EC-Earth_epc100_change.png')
D <- readPNG('GFDL_epc100_change.png')
E <- readPNG('MPI_epc100_change.png')
f <- readPNG('UKESM_epc100_change.png')

grid.combine <- grid.arrange(rasterGrob(A),rasterGrob(B),rasterGrob(C),
                             rasterGrob(D),rasterGrob(E),rasterGrob(f),ncol=2, nrow=3)

ggsave(grid.combine, filename = "faceted_epc100_avg.png", device = "png", path = "~/senior_thesis/figures/", 
       dpi = 500, width = 16, height = 12, units = "cm")

```

Calculate maximum annual MLD in the short-term (2014-2034) and long-term (2077-2097) units: m
```{r}
setwd("~/senior_thesis/")
source('calc_MLD_max.R')

##CESM -----------
get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'mlotst_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc')

calc_MLD_max(wd = "~/senior_thesis/combined_CESM_files", 
            nc.file= 'mlotst_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc',
            seq.start.st = 17, 
            seq.start.lt = 774,
            model.name = "CESM")

##CMCC ------------
get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'mlotst_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc')


calc_MLD_max(wd = "~/senior_thesis/combined_CMCC_files", 
            nc.file= 'mlotst_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc',
            seq.start.st = 2, 
            seq.start.lt = 759,
            model.name = "CMCC")

##EC-Earth ----------
get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/",
         file.name = 'mlotst_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc')

calc_MLD_max(wd = "~/senior_thesis/combined_EC-Earth_files", 
            nc.file= 'mlotst_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc',
            seq.start.st = 1, 
            seq.start.lt = 757,
            model.name = "EC-Earth")

##GFDL ----------
get_time(data.path = "~/senior_thesis/combined_GFDL_files/",
         file.name = 'mlotst_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc')

calc_MLD_max(wd = "~/senior_thesis/combined_GFDL_files", 
            nc.file= 'mlotst_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc',
            seq.start.st = 2, 
            seq.start.lt = 759,
            model.name = "GFDL")

## MPI --------------
get_time(data.path = "~/senior_thesis/combined_MPI_files/",
         file.name = 'mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc')

calc_MLD_max(wd = "~/senior_thesis/combined_MPI_files", 
            nc.file= 'mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc',
            seq.start.st = 1, 
            seq.start.lt = 697,
            model.name = "MPI")

## UKESM -------- come back and troubleshoot this
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'mlotst_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc')

calc_MLD_max(wd = "~/senior_thesis/combined_UKESM_files", 
            nc.file= 'mlotst_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc',
            seq.start.st = 30, 
            seq.start.lt = 785,
            model.name = "UKESM")
```

Plot 3 panel figure showing short-term (2014-2034), long-term (2079-2099), and difference in average maximum annual MLD
```{r}
setwd("~/senior_thesis/")
source('plot_MLD_max.R')

#CESM
plot_MLD_max(wd = "~/senior_thesis/combined_CESM_files",
             nc.file = 'mlotst_Omon_CESM2_ssp585_r10i1p1f1_gn_201501-210012.nc',
             model.name = "CESM",
             lat.name = "nlat",
             lon.name = "nlon")

#CMCC
plot_MLD_max(wd = "~/senior_thesis/combined_CMCC_files",
             nc.file = 'mlotst_Omon_CMCC-ESM2_ssp585_r1i1p1f1_gn_201501-210012.nc',
             model.name = "CMCC",
             lat.name = "latitude",
             lon.name = "longitude")

#EC-Earth
plot_MLD_max(wd = "~/senior_thesis/combined_EC-Earth_files",
             nc.file = 'mlotst_Omon_EC-Earth3-CC_ssp585_r1i1p1f1_gn_201501-210012.nc',
             model.name = "EC-Earth",
             lat.name = "latitude",
             lon.name = "longitude")

#GFDL
plot_MLD_max(wd = "~/senior_thesis/combined_GFDL_files",
             nc.file = 'mlotst_Omon_GFDL-ESM4_ssp585_r1i1p1f1_gr_201501-210012.nc',
             model.name = "GFDL",
             lat.name = "lat",
             lon.name = "lon")

#MPI - again, this plots upside down, so uncomment the lines in the function
plot_MLD_max(wd = "~/senior_thesis/combined_MPI_files",
             nc.file = 'mlotst_Omon_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_201501-210012.nc',
             model.name = "MPI",
             lat.name = "latitude",
             lon.name = "longitude")

#UKESM
plot_MLD_max(wd = "~/senior_thesis/combined_UKESM_files",
             nc.file = 'mlotst_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-210012.nc',
             model.name = "UKESM",
             lat.name = "latitude",
             lon.name = "longitude")

```

Plot 6 panel figure showing change in MLDmax for all 6 models
```{r}
#run this in a R script, for some reason readPNG doesn't work in the notebook

setwd("~/senior_thesis/figures/")
A <- readPNG('CESM_MLDmax_change.png')
B <- readPNG('CMCC_MLDmax_change.png')
C <- readPNG('EC-Earth_MLDmax_change.png')
D <- readPNG('GFDL_MLDmax_change.png')
E <- readPNG('MPI_MLDmax_change.png')
f <- readPNG('UKESM_MLDmax_change.png')

grid.combine <- grid.arrange(rasterGrob(A),rasterGrob(B),rasterGrob(C),
                             rasterGrob(D),rasterGrob(E),rasterGrob(f),ncol=2, nrow=3)

ggsave(grid.combine, filename = "faceted_MLDmax.png", device = "png", path = "~/senior_thesis/figures/", 
       dpi = 500, width = 16, height = 12, units = "cm")

```


Calculate POC flux at the MLDmax
```{r}
setwd("~/senior_thesis/")
source('libraries.R')
source('calc_expc_avg_new.R')
source('calc_expc_avg_st.R')
source('calc_expc_avg_lt.R')
source('get_time.R')

#every model but UKESM was averaged from 2015-2035 and 2079-2099, UKESM was 2015-2035 and 2077-2097

## CESM --------------

#start = 03/01/14, end = 02/08/99
get_time(data.path = "~/senior_thesis/combined_CESM_files/",
         file.name = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc')

#Short term start: 03/01/15
calc_expc_avg_st(wd = "~/senior_thesis/combined_CESM_files",
              nc.file = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc',
              model.name = "CESM",
              start.st = 2,
              lon.length = 1:320,
              lat.length = 1:384)

#Long term start: 02/13/79
calc_expc_avg_lt(wd = "~/senior_thesis/combined_CESM_files",
              nc.file = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc',
              model.name = "CESM",
              start.lt = 66,
              lon.length = 1:320,
              lat.length = 1:384)

#new attempt
calc_expc_avg(wd = "~/senior_thesis/combined_CESM_files",
              nc.file = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc',
              model.name = "CESM",
              start.st = 2,
              start.lt = 66,
              lon.length = 1:320,
              lat.length = 1:384)


## CMCC ----------------

#start = 05/23/15, end = 05/02/00
get_time(data.path = "~/senior_thesis/combined_CMCC_files/",
         file.name = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc')

#Short term start 05/23/15
calc_expc_avg_st(wd = "~/senior_thesis/combined_CMCC_files",
              nc.file = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "CMCC",
              start.st = 1,
              lon.length = 1:362,
              lat.length = 1:292)

#Long term start: 05/07/79
calc_expc_avg_lt(wd = "~/senior_thesis/combined_CMCC_files",
              nc.file = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "CMCC",
              start.lt = 65,
              lon.length = 1:362,
              lat.length = 1:292)

calc_expc_avg(wd = "~/senior_thesis/combined_CMCC_files",
              nc.file = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "CMCC",
              start.st = 1,
              start.lt = 65,
              lon.length = 1:362,
              lat.length = 1:292)

##EC-Earth ----------

#start = 07/02/15, 07/02/00
get_time(data.path = "~/senior_thesis/combined_EC-Earth_files/", file.name = 'expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc')

#Short term start: 07/02/15
calc_expc_avg_st(wd = "~/senior_thesis/combined_EC-Earth_files",
              nc.file = 'expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "EC-Earth",
              start.st = 1, 
              lon.length = 1:362,
              lat.length = 1:292)

#Long term start: 07/02/79
calc_expc_avg_lt(wd = "~/senior_thesis/combined_EC-Earth_files",
              nc.file = 'expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "EC-Earth",
              start.lt = 65,
              lon.length = 1:362,
              lat.length = 1:292)

calc_expc_avg(wd = "~/senior_thesis/combined_EC-Earth_files",
              nc.file = 'expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "EC-Earth",
              start.st = 1,
              start.lt = 65,
              lon.length = 1:362,
              lat.length = 1:292)

##GFDL -------

get_time(data.path = "~/senior_thesis/combined_GFDL_files/", file.name = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc')

#Short term start: 05/23/15
calc_expc_avg_st(wd = "~/senior_thesis/combined_GFDL_files",
              nc.file = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc',
              model.name = "GFDL",
              start.st = 1,
              lon.length = 1:360,
              lat.length = 1:180)

#Long-term start: 05/07/79
calc_expc_avg_lt(wd = "~/senior_thesis/combined_GFDL_files",
              nc.file = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc',
              model.name = "GFDL",
              start.lt = 65,
              lon.length = 1:360,
              lat.length = 1:180)

calc_expc_avg(wd = "~/senior_thesis/combined_GFDL_files",
              nc.file = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc',
              model.name = "GFDL",
              start.st = 1,
              start.lt = 65,
              lon.length = 1:360,
              lat.length = 1:180)
##MPI --------

#start = 07/02/15, end = 07/02/00
get_time(data.path = "~/senior_thesis/combined_MPI_files/", file.name = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc')

#07/02/15
calc_expc_avg_st(wd = "~/senior_thesis/combined_MPI_files",
              nc.file = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "MPI",
              start.st = 1, 
              lon.length = 1:802,
              lat.length = 1:404)

#07/02/79
calc_expc_avg_lt(wd = "~/senior_thesis/combined_MPI_files",
              nc.file = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc',
              model.name = "MPI",
              start.lt = 65,
              lon.length = 1:802,
              lat.length = 1:404)


##UKESM ----------

#UKESM get time long-term, start = 03/04/47, end = 05/10/97
get_time(data.path = "~/senior_thesis/combined_UKESM_files/",
         file.name = 'expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_205001-210012.nc')
#UKESM get time short-term, start = 09/03/12, end = 02/02/47
get_time(data.path = "~/senior_thesis/UKESM_data/",
         file.name = 'expc_Omon_UKESM1-0-LL_ssp585_r1i1p1f2_gn_201501-204912.nc')

#custom calculation for UKESM since I had to take the yearly average within the calc_expc_avg function
source('calc_expc_st_UKESM.R')
source('calc_expc_lt_UKESM.R')

```

Plot 3 panel figure showing short-term (2015-2035), long-term (2079-2099), and difference in average POC flux at the MLDmax
```{r}
setwd("~/senior_thesis/")
source('plot_expc_avg.R')

#CESM
plot_expc_avg(wd = "~/senior_thesis/combined_CESM_files",
             nc_file = 'expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc',
             model.name = "CESM",
             lat.name = "nlat",
             lon.name = "nlon")

#CMCC
plot_expc_avg(wd = "~/senior_thesis/combined_CMCC_files",
             nc_file = 'expc_Oyr_CMCC-ESM2_ssp585_r1i1p1f1_gn_2015-2100.nc',
             model.name = "CMCC",
             lat.name = "latitude",
             lon.name = "longitude")

#EC-Earth
plot_expc_avg(wd = "~/senior_thesis/combined_EC-Earth_files",
             nc_file = 'expc_Oyr_EC-Earth3-CC_ssp585_r1i1p1f1_gn_2015-2100.nc',
             model.name = "EC-Earth",
             lat.name = "latitude",
             lon.name = "longitude")

#GFDL
plot_expc_avg(wd = "~/senior_thesis/combined_GFDL_files",
             nc_file = 'expc_Oyr_GFDL-ESM4_ssp585_r1i1p1f1_gr_2015-2100.nc',
             model.name = "GFDL",
             lat.name = "latitude",
             lon.name = "longitude")

#MPI
plot_expc_avg(wd = "~/senior_thesis/combined_MPI_files",
             nc_file = 'expc_Oyr_MPI-ESM1-2-HR_ssp585_r1i1p1f1_gn_2015-2100.nc',
             model.name = "MPI",
             lat.name = "latitude",
             lon.name = "longitude")
```

Plot depth profiles in various locations
```{r}
setwd("~/senior_thesis/combined_CESM_files/")
nc_data <- nc_open('expc_Oyr_CESM2_ssp585_r10i1p1f1_gn_2015-2100.nc')

#NOTE: this section won't run in the notebook, so paste these lines into a script and run first before sourcing function

#get expc in 2014-2034
variable.st <- ncvar_get(nc_data,"expc",start= c(1,1,1,1), count = c(-1,-1,-1,20))

#get expc in 2079-2099
variable.lt <- ncvar_get(nc_data,"expc",start= c(1,1,1,66), count = c(-1,-1,-1,20))

#calcuates short-term average POC flux over 20 years, still including the entire water column averages
avg_expc_st <- apply(variable.st,c(1,2,3),mean,na.rm=TRUE)

#calcuates short-term average POC flux over 20 years, still including the entire water column averages
avg_expc_lt <- apply(variable.lt,c(1,2,3),mean,na.rm=TRUE)

#saves these arrays as .rds files so they are easier to load next time I need them
setwd("~/senior_thesis/plotting_dataframes/")
saveRDS(avg_expc_st, file = "avg_expc_st.Rds", ascii = TRUE)
saveRDS(avg_expc_lt, file = "avg_expc_lt.Rds", ascii = TRUE)

#end section

source('~/senior_thesis/depth_profiles.R')

#load short-term and long-term average POC flux arrays
avg_expc_st <- readRDS("~/senior_thesis/plotting_dataframes/avg_expc_st.Rds")  
avg_expc_lt <- readRDS("~/senior_thesis/plotting_dataframes/avg_expc_lt.Rds")

# LABRADOR SEA 
profile_create(grid.cell = c(305,355), depth.range = c(3000,0), expc.range = c(0,4), 
               title = "a) Labrador Sea",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "labrador_sea_depth_profile")

# EQUATORIAL EASTERN PACIFIC
profile_create(grid.cell = c(274,184), depth.range = c(3200,0), expc.range = c(0,13), 
               title = "c) Equatorial Eastern Pacific",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "equatorial_eastern_pacific_depth_profile")

# SOUTHERN OCEAN
profile_create(grid.cell = c(99,63), depth.range = c(3000,0), expc.range = c(0,4), 
               title = "e) Southern Ocean",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "southern_ocean_depth_profile")

# SUBTROPICAL INDIAN OCEAN (not using in thesis)
profile_create(grid.cell = c(120,150), depth.range = c(5000,0), expc.range = c(0,4), 
               title = "Subtropical Indian Ocean",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "subtropical_indian_ocean_depth_profile")

# ICELAND BASIN
profile_create(grid.cell = c(30,352), depth.range = c(1200,0), expc.range = c(0,5), 
               title = "b) Iceland Basin",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "iceland_basin_depth_profile")

#SUBTROPICAL NORTH PACIFIC
profile_create(grid.cell = c(230,275), depth.range = c(5000,0), expc.range = c(0,1.5), 
               title = "d) Subtropical North Pacific",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "subtropical_north_pacific_depth_profile")

# BELLINGHAUSEN SEA
profile_create(grid.cell = c(276,21), depth.range = c(3300,0), expc.range = c(0,2), 
               title = "f) Bellingshausen Sea",
               data.path = "~/senior_thesis/combined_CESM_files/", 
               save.path = "~/senior_thesis/depth_profiles",
               save.name = "bellinghausen_sea_depth_profile")

#arranging into 6 panel figure (NOTE: run this in a separate script, there's a glitch in readPNG)
setwd("~/senior_thesis/depth_profiles/")
A <- readPNG('labrador_sea_depth_profile.png')
B <- readPNG('iceland_basin_depth_profile.png')
C <- readPNG('equatorial_eastern_pacific_depth_profile.png')
D <- readPNG('subtropical_north_pacific_depth_profile.png')
E <- readPNG('southern_ocean_depth_profile.png')
f <- readPNG('bellinghausen_sea_depth_profile.png')

grid.combine <- grid.arrange(rasterGrob(A),rasterGrob(B),rasterGrob(C),
                             rasterGrob(D),rasterGrob(E),rasterGrob(f),ncol=2, nrow=3)

ggsave(grid.combine, filename = "faceted_depth_profiles.png", device = "png", path = "~/senior_thesis/depth_profiles/", 
       dpi = 500, width = 16, height = 22, units = "cm")

```

Organizing depth profile output for table info
```{r}
#combine table output csv files into one file
files <- list.files("~/senior_thesis/depth_profiles/", pattern = "*.csv$")
setwd("~/senior_thesis/depth_profiles/")
read.files <- lapply(files,read_csv)
binded_file <- rbindlist(read.files, fill = TRUE)
write.csv(binded_file, "table_info.csv")

```

Calculate global POC flux at 100m
```{r}

#downloading CESM cell area files
save.path <- "~/senior_thesis/cmip6_data"

cmip6.index <- "http://esgf-data.ucar.edu/thredds/fileServer/esg_dataroot/CMIP6/ScenarioMIP/NCAR/CESM2/ssp585/r10i1p1f1/Ofx/areacello/gn/v20200528/areacello_Ofx_CESM2_ssp585_r10i1p1f1_gn.nc"


get_nc_thredds(cmip6.index, save.path)

setwd("~/senior_thesis/cmip6_data")
nc_data <- nc_open('areacello_Ofx_CESM2_ssp585_r10i1p1f1_gn.nc')

#get file metadata
sink('areacello_Ofx_CESM2_ssp585_r10i1p1f1_gn.txt')
print(nc_data)
setwd(save.path)
sink()

#get longitude and latitude
lon <- ncvar_get(nc_data, "nlon")
lat <- ncvar_get(nc_data, "nlat")

#get area
area <- ncvar_get(nc_data, "areacello")

#read in global POC flux at 100m data
epc100_avg_st <- readRDS("~/senior_thesis/plotting_dataframes/epc100_avg_st.Rds")
epc100_avg_lt <- readRDS("~/senior_thesis/plotting_dataframes/epc100_avg_lt.Rds")

global_flux_st <- epc100_avg_st*area

sum_st <- sum(global_flux_st, na.rm = TRUE)

#SHORT TERM total global POC flux in Pt C / yr = 7.12
sum_st <- sum_st*12.01/1000000000000000

global_flux_lt <- epc100_avg_lt*area

sum_lt <- sum(global_flux_lt, na.rm = TRUE)

#LONG TERM total global POC flux in Pt C / yr = 6.81
sum_lt <- sum_lt*12.01/1000000000000000

percent_change <- (sum_st-sum_lt)/sum_st*100

```

Formatting data for plotting POC flux transects
```{r}

#Atlantic Transect
calc_transect(lon = 10, save.name.st = "lon10_transect_st", save.name.lt = "lon10_transect_lt")

#Pacific Transect
calc_transect(lon = 205, save.name.st = "lon205_transect_st", save.name.lt = "lon205_transect_lt")

```

Plotting POC flux transects
```{r}
#loading objects
atlantic_st <- readRDS("~/senior_thesis/plotting_dataframes/lon10_transect_st.Rds")
atlantic_lt <- readRDS("~/senior_thesis/plotting_dataframes/lon10_transect_lt.Rds")
pacific_st <- readRDS("~/senior_thesis/plotting_dataframes/lon205_transect_st.Rds")
pacific_lt <- readRDS("~/senior_thesis/plotting_dataframes/lon205_transect_lt.Rds")
mean_MLD_max_2079_2099 <- readRDS("~/senior_thesis/plotting_dataframes/mean_MLD_max_2079_2099.Rds")
mean_MLD_max_2014_2033 <- readRDS("~/senior_thesis/plotting_dataframes/mean_MLD_max_2014_2033.Rds")

#I haven't fixed the title aspect of the plot_transect function, so be sure to change this manually before generating figures

#3 panel atlantic transect, full depth and zoomed in
plot_transect(lon = 10,
              save.name = "Atlantic_transect.png",
              save.name.zoom = "Atlantic_transect_1000m.png",
              transect.st = atlantic_st,
              transect.lt = atlantic_lt)

#3 panel pacific transect, full depth and zoomed in
plot_transect(lon = 205,
              save.name = "Pacific_transect.png",
              save.name.zoom = "Pacific_transect_1000m.png",
              transect.st = pacific_st,
              transect.lt = pacific_lt)


```


